---
title: "Small-Body Objects of the Solar System"
author: "Gabor Simon"
date: "2017-12-24"
output:
    html_document:
        self_contained: false

---

## About

The solar system contain a lot of small-body objects (like asteroids and comets), whose characteristics are well charted.
Here we visualise only the objects whose diameter is at least 20 kms, and display only the following attributes:

- IAU name
- diameter (km)
- eccentricity 
- semi-major axis of the orbit (au)
- perihelion distance (au)
- inclination (deg)
- orbit period (yr)

The input data was generated by the [JPL Small-Body Database Search Engine](https://ssd.jpl.nasa.gov/sbdb_query.cgi), with the filter of `diameter >= 20` and selecting the fields `IAU name, diameter, e, a, q, i, period (years)`.

(For a concise output the outliers are discarded.)

Our chart displays the semi-major axis of the orbit on the X axis, perihelion distance on Y, the diameter as the blob size, and the orbit periodicity as colour.

Hovering the cursor on an object, the details are displayed in a popup.

You can zoom/pan/select any part of the chart using the Plotly icons.

The source GitHub repository is accessible [here](https://github.com/gsimon75/SolarSystemSmallBodies),
the online viewable HTML page [here](https://gsimon75.github.io/SolarSystemSmallBodies).

## The chart

```{r, message=F, warning=F}
library(plotly)
```

```{r}
sb <- read.csv("solar_sb_20km.csv")

# quantile range for objects to keep
bracket <- c(0.2, 0.8)
a_bracket <- quantile(sb$a, probs=bracket)

# discard outliers, use meaningful names
sb <- sb %>%
	filter(a_bracket[[1]] <= a & a <= a_bracket[[2]]) %>%
	transmute(name, diameter, eccentricity=e, semi.major.axis=a, perihelion=q, inclination=i, period=per_y) 

# generate popup info strings
sb$hover <- with(sb, paste(name,
		"<br>diameter=", diameter,
		"<br>eccentricity=", eccentricity,
		"<br>semi-major axis=", semi.major.axis,
		"<br>perihelion=", perihelion,
		"<br>inclination=", inclination,
		"<br>period=", period))

# generate the chart
plot_ly(sb, type="scatter", mode="markers", x=~semi.major.axis, y=~perihelion, size=~diameter, color=~period, text=~hover)
```

